---
title: "Getting Started with Binomial Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

##Binomial

The package `'binomial'` is to implement functions for calculating probabilities 
of a Binomial random variable, as well as other relevant calculations such as 
probability distribution, expected value, variance, kurtosis, skewness, etc.

##Important things to note
Before you start implementign this package, make sure your distribution is **binomial**.

Definition of binomial distribution: the discrete probability distribution 
of the k number of successes in a sequence of n independent experiments, each with 
its own outcomes of success or failure.

##Binomial Choose
The first step of calculating binomial probability is to know the success(k) and 
trials(n) of your probability.

Here, we use the `bin_choose(n, k)` functions to calculate the number of combinations 
in which k successes can occur in n trials.

For example, if k = 2, n = 5

```{r}
combo <- bin_choose(n = 5, k = 2)
combo
```

*This function could halt if your k is bigger than n, making it an invalid input.*

##Probability of success
After we calculate the number of combinations to achieve k successec in n trials, we 
can then calculate the probability of such successes appearing. Using the 
`bin_probability` function, we are able to calculate the probability of such binomial
distribution.

Here are a few examples of invoking `bin_probability(success, trials, prob)`:
```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5) 
bin_probability(success = 2, trials = 5, prob = 0.5)

# probabilities of getting 2 or less successes in 5 trials 
# (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)

# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)
```

*This function would error if any of the inputs are invalid.*

##Distribution of probability
After we calculate the probability of k successes in n trials, we can then construct 
the distribution of probability in a dataframe with varying number of successes using 
the function `bin_distriibutioin(trials, prob)`. 
It returns a table of valid successes and each of their probability occuring.

Here's an example:
```{r}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```

The returned object has a class of 'bindis' (binomial distribution) and 'data.frame'.
The first column has *success* and the second column has *probability*.

###Plotting the distribution
Using an unique plot function just for the class 'bindis', we can construct a bar plot
of the distribution.

Here's an example:
```{r}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5) 
plot(dis1)
```

**Note**: you don't need to say `plot.bindis`. Just saying `plot` would be sufficient 
because 
R is able to identify the class of the object and call the corresponding plot function.

##Cumulative distribution
We can build on top of the distribution of probability to calculate the cumulative 
probability using the `bin_cumulative(trials, prob)` function:

```{r}
# binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
```

The returned object is a class of 'bincum' (binomial cumulative distribtuion) 
and 'data.frame'.
The first column has *success*, the second column has *probability*, and the third
column has *cumulative*.

###Plotting cumulative distrbution
Using an unique plotting function just for the class 'bincum', we can construct a line
and point graph:
```{r}
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5) 
plot(dis2)
```

**Note**: you don't need to say `plot.bincum`. Just saying `plot` would be sufficient 
because 
R is able to identify the class of the object and call the corresponding plot function.


##Create a binomial random variable object
This function creates a binomial random variable object with a class of 'binvar'.
```{r}
bin_variable(trials = 10, p = 0.3)
```

###Print the object
You can print the object by using the `print()` function:
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

###Creating and printing a summary object 
You can use the `summary.binvar()` functioin to create summay of the binomial random
variable that contains trials, prob, mean, variance, mode, skewness, and kurtosis.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
binsum1 <- summary(bin1)
binsum1
```

##Summary functions

We also have individual functions to calculate the mean, variance, mode, skewness, and
kurtosis of the binomial random variable using these functioins:
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

*This function would error if any of the inputs are invalid.*

