---
title: "Binomial Package README"
author: "Zichen Zhao"
date: "5/3/2019"
output: 
  github_document:
    html_preview: false
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

##Overview

`'binomial'` is a minimal package to implement functions for calculating probabilities 
of a Binomial random variable, as well as other relevant calculations such as 
probability distribution, expected value, variance, kurtosis, skewness, etc.

* `bin_mean()` calculates the mean of the binomial distribution
* `bin_variance()` calculates the mean of the binomial distribution
* `bin_mode()` calculates the mean of the binomial distribution
* `bin_skewness()` calculates the mean of the binomial distribution
* `bin_kurtosis()` calculates the mean of the binomial distribution
* `bin_choose()` calculates the number of combinations in which k successes can occur 
in n trials.
* `bin_probability()` calculates the probability in which k successes can occur in n trials.
* `bin_distribution()` constructs a table of successes and probability.
* `bin_cumulative()` constructs a table of successes, probability, and cumulative probability.
* `bin_variable()` creates the binomial random variable object
* `plot()` plot the specific graph according to the class of the object
* `summary()` summarizes the probability of distribution

##Motivation

This package has been developed to illustrate some calculations in binomial random variable.

##Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("zichenz/binomial")
# install "cointoss" (with vignettes)
devtools::install_github("ichenz/binomial", build_vignettes = TRUE)
```
##Usage
```{r}
library(binomial)
#Calculating probability of binomial random variable
bin_choose(n = 5, k = 3)
bin_probability(3, 5, 0.5)

#Creating a distribution and plotting
dis1 <- bin_distribution(5, 0.5)
plot(dis1)

#Creating a cumulative table and plotting
dis2 <- bin_cumulative(5, 0.5)
plot(dis2)

#Creating a binomial random variable object and its related functions
bin1 <- bin_variable(trials = 5, p = 0.5)
bin1
binsum1 <- summary(bin1)
binsum1
```
